%-------------------------
% Resume in Latex
% Author : Jose Vega
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/josevegar}{\Large José E. Vega Raymondi}} & Email : \href{mailto:jvegar@uni.pe}{jvegar@uni.pe}\\
  \href{https://github.com/jvegar}{https://github.com/jvegar} & Mobile : +51-991139451 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of the Pacific}{Lima, Perú}
      {Master in Finance - Invesment Portfolio Management}{Dic. 2014 -- Dic. 2016}
    \resumeSubheading
      {National University of Engineering}{Lima, Perú}
      {Bachelor in Systems Engineering}{Ene. 2003 -- Dic. 2009}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {BairesDev}{California, USA (Remote)}
  {Software Engineer}{Sept 2021 - Today}
  \resumeItemListStart
    \resumeItem{Backend Development}
      {DB Modeling (Postgres), API Development (Node, JS, TypeScript, GraphQL, REST), Frameworks (NestJS, Express, Apollo Server, Hapi)}
    \resumeItem{Front-End Development}
      {UI Prototyping (Figma), UI Components Development (Angular, React, HTML, CSS, JS, TypeScript).}
    \resumeItem{DevOps}
      {Agile Board (Jira), Git Repositories (GitLab, Azure Devops), Pipelines (Azure Devops), Docker containers.} 
  \resumeItemListEnd

  \resumeSubheading
  {NTT Data}{Lima, Perú}
  {Centers Lead Developer}{Sept 2020 - Aug 2021}
  \resumeItemListStart
    \resumeItem{Leadership}
      {Mentoring junior members of the team, evaluating development work efforts and quality.}
    \resumeItem{Backend Development}
      {DB Modelling (SQL Server), MVC Application Development (CSharp), REST Service Development (CSharp, NodeJS, Express).}
    \resumeItem{Front-End Development}
      {UI Prototyping (Justinmind), SPA Development (HTML, CSS, JS, TypeScript), JS Frameworks (React, AngularJS).}
    \resumeItem{DevOps}
      {Agile Board (MS Planner), Git Repositories (Azure Devops), Pipelines (Azure Devops)}
   
  \resumeItemListEnd

    \resumeSubheading
      {Certero}{Lima, Perú}
      {Solutions Architect}{Feb 2017 - Mar 2020}
      \resumeItemListStart
        \resumeItem{Data Architecture}
          {DB Modelling (SQL Server), ETL development (SSIS, Azure Data Factory), Dashboard designing (PowerBI).}
        \resumeItem{Web Application Development Full Stack}
          {Forms Design and Prototyping (Visio, Justinmind), Front-End Components Development (HTML,CSS,TypeScript, NodeJS, React), MVC .NET Application Development.}          
        \resumeItem{Applications Architecture}
          {Business and Application Layer Design (BMPN), REST APIs Consuming and Building (.NET Core, NodeJS).}
        \resumeItem{DevOps}
          {Agile Board (Trello), Git Repositories (Gitlab), Containerization (Docker).}
        \resumeItem{Cloud Architecture}
          {Cloud Components Design (Azure), Script automating (Azure Cli, Powershell)}.    
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Evol TS Net}{ Lima, Perú}
      {Developer Consultant}{Ene 2014 - Ene 2017}
      \resumeItemListStart
        \resumeItem{Backend Development}
          {Building SharePoint server-side components (webparts, event receivers, timer jobs). MVC Application development and WCF Services for integration with SAP.}
        \resumeItem{Database}
          {Database modelling. DB Components Building (T-SQL). Queries optimization (indexes, temp tables).}        
        \resumeItem{Front-End Development}
          {Redesigning Front-end components (master pages) for an Intranet using UX Design methodologies, responsive design (Bootstrap) and JS Libraries (JQuery, Knockout).} 
      \resumeItemListEnd

    \resumeSubheading
      {CGI}{Lima, Perú}
      {Developer}{Dic 2011 - Dic 2013}
      \resumeItemListStart
        \resumeItem{Backend Development}
          {Application Server Optimization (IIS), and building new server-side components (webparts, powershell scripts, WCF services).}
        \resumeItem{Database}
          {Building ETLs for integration between databases and Flat CSV files (SQL Server).}
      \resumeItemListEnd
%
%    \resumeSubheading
%      {Banco de la Nación}{Lima, Perú}
%      {IT Infrastructure Analyst}{Jun 2009 - Jul 2011}
%      \resumeItemListStart
%        \resumeItem{IBM Portal Server}
%          {Building Portlets and SOAP Web Services using Java.}
%        \resumeItem{IBM Business Process Manager}
%          {Implementing Proof of Concepts for process automation.}
%      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Implementation of Case Manager - Lucinity}
      {Build GraphQL APIs using TypeScript, Express, Apollo Server with Node and custom React components for Case Manager application.}
    \resumeSubItem{Migration of Learning Portal - Instructure}
      {Migrated backend built in Node v5 to v16. Updated SQL migration files from Postgrest v9 to v12. Replaced deprecated JS packages. Refactored code to use new ES6 features (let/const, promises, async/await)}
    \resumeSubItem{Implementation of custom institutional portal - Fonafe}
      {Developing custom Content Management System using .NET Core, REST APIs, and MVC for Backend, and Angulas JS and Bootstrap for FrontEnd.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
      \resumeSubItem{Languages}{: TypeScript, Javascript, CSharp, Java, Python }          
      \resumeSubItem{Frameworks}{: Express, NestJS, Apollo GraphQL, Hapi, Net Core, Spring Boot}      
      \resumeSubItem{Methodologies}{: Waterfall, Agile, Kanban, DevOps}      
      \resumeSubItem{Idioms}{: Spanish - Native / English - C1 Advanced} 
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}